Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-04 doc/main_jfm.tex
updates

For a two-dimensional vesicle, we denote a constant initial radius $R_0$
and the dimensionless shear rate is
\begin{align}
  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the shear rate, $\kappa$ the bending rigidity, and
$\mu$ the fluid viscosity~\cite{Finken08}.

@@

\begin{figure}
\centering
\includegraphics[height=2in]{relax.eps}
\includegraphics[height=2in]{relax2.eps}
  \todo[inline]{Put pressure of each of the two configurations below
  this.}
  \caption{Vesicle relaxes under a quiescent flow. (a) The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay. (b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
  }
    \label{figure2}
\end{figure}

@@

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_shear_0.pdf}
\includegraphics[height=1.2in]{N116_shear_3000.pdf}
\includegraphics[height=1.2in]{N116_shear_6000.pdf}
\includegraphics[height=1.2in]{N116_shear_9000.pdf}\\
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
  }
    \label{figure9}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2.in]{N116_ext_0.pdf}
\includegraphics[height=2.in]{N116_ext_2500.pdf}\\
\includegraphics[height=2.in]{N116_ext_5000.pdf}
\includegraphics[height=2.in]{N116_ext_7500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple.
  }
    \label{figure8}
\end{figure}

>>>>

@@

\begin{figure}
\centering
\includegraphics[height=2in]{relax.eps}
\includegraphics[height=2in]{relax2.eps}\\
\includegraphics[height=2.in]{N58_0pres.pdf}
\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
  \caption{Vesicle relaxes under a quiescent flow. (a) The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay. (b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
  }
    \label{figure2}
\end{figure}

@@

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and we set the force is scaled from the 
interfacial tension $\gamma=4.1$ pN nm. We then be able to calculate the corresponding 
time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
$\kappa=8.51$ kT $\approx35$ pN nm.

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0$ and the dimensionless shear rate 
is referred from~\cite{Finken08}
\begin{align}
  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu=1$ cP the fluid viscosity is used through this work.

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_shear_0.pdf}
\includegraphics[height=1.2in]{N116_shear_2500.pdf}
\includegraphics[height=1.2in]{N116_shear_5000.pdf}
\includegraphics[height=1.2in]{N116_shear_7500.pdf}\\
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
  }
    \label{figure9}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2.in]{N116_ext_0.pdf}
\includegraphics[height=2.in]{N116_ext_2000.pdf}\\
\includegraphics[height=2.in]{N116_ext_4000.pdf}
\includegraphics[height=2.in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple.
  }
    \label{figure8}
\end{figure}
